Trends of SDR in Thessaloniki

### 2023-07-14 Article.Rmd
Commit 2023-07-14 20:14
Commit 2023-07-14 21:09

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}

output: 
  rticles::elsevier_article:
    keep_tex:         no
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  bookdown::word_document2: default
# date:           "`r format(Sys.time(), '%F')`"
---

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near the horizon, we have to exclude all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, comes from NOAA [@Coddington2005], it overlaps with our data, and is interpolated to match with the time step of the data.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->
As a result, we can present all radiation data as a fraction of Sun's TSI. 
After the preparation of the data, we have $`r SDR_N_All`$  1-minute measurements, of which,
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$ 
are characterized with clear-sky condition, and the rest 
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
with cloud-sky conditions.

<!-- aggregation -->
In order to investigate the SDR trend, we implement an appropriate aggregation scheme of the 1-minute data to a coarser time scale. To preserve the representativeness we are using the following criteria:
a) for daily mean values we exclude days with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily means, and months with less than `r Monthly_aggegation_N_lim` days are omitted. 
To create the daily and monthly seasonal values, we group the data based on the day of year number, and the corresponding calendar month respectively.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by the corresponding season (Winter: December - February, Spring: March - May, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
<!-- SZA Deseasonalization -->
To estimate Sun's SZA contribution to the SDR brightening, the 1-minute data were aggregate in $1^\circ$ SZA bins, separated for instances before and after the local noon, and then was deseasonalized as above. 
Thus, for each dataset we have obtained the relative departure of the seasonal mean.

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  rticles::elsevier_article:
    keep_tex:         no
    citation_package: natbib
# date:           "`r format(Sys.time(), '%F')`"
---

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near the horizon, we have to exclude all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all one-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, comes from NOAA [@Coddington2005], and were interpolated to match with the time step of our measurements. 
The final dataset contains
$`r SDR_N_All`$
one-minute measurements, of which,  $`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$
correspond to clear-sky conditions and 
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
to cloud-sky conditions.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->

<!-- aggregation -->
In order to investigate the SDR trends, we implemented an appropriate aggregation scheme to the 1-minute data to derive series in coarser time scales.
To preserve the representativeness of the data we used the following criteria: 
a) for daily mean values we exclude days with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values were computed from daily means
only when at least `r Monthly_aggegation_N_lim` days were available.
To create the daily and monthly climatological means, we averaged the data based on the day of year and calendar month, respectively.
<!-- Seasonal -->
For the seasonal means we averaged the mean daily values in each season (Winter: December - February, Spring: March - May, etc.).
<!-- Deseasonalization -->
Finally, each data set was deseasonalized by subtracting the corresponding climatological annual cycle (daily or monthly) from the actual data.  
To estimate SZA contribution to the SDR trends, the one-minute data were aggregated the data in $1^\circ$ SZA bins, separately for the morning and afternoon hours, which were then deseasonalized as mentioned above.

a) for daily mean values we excluded days with less
than 
[This is not a good criterion! It must be seasonal and 2 hours of
data are not enough for the calculation of daily means.\
How about: "excluded days with more than 180 missing i-minute values
during daylight hours".]{.comment-start id="6" author="Alkis Bais"
date="2023-07-14T07:52:00Z"}180 valid data points[]{.comment-end
id="6"},
